ICH Laterality

### 2024-03-06 manuscripts/index.qmd
manuscript actually started

---
title: Differences in care for patients with left vs. right hemisphere intracerebral hemorrhage
authors:
  - name: Nikhil Patel
    orcid: 0000-0002-3193-8590
    affiliation: Department of Neurology, Wake Forest School of Medicine
    email: nikhil.patel@atriumhealth.org
    roles: writing
    corresponding: true
  - name: Rahul Karamchandani
    affiliation: Department of Neurology, Wake Forest School of Medicine
    corresponding: false
    roles: writing
bibliography: references.bib
---

## Section

This is a simple placeholder for the manuscript's main document [@audetat_diagnosis_2017-1].

>>>>

---
title: "ICH Laterality"
subtitle: "Project Website"
---

This is the landing page for the website.
